I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-11-18 paper_io_sim.tex
some comments"

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}

@@

\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:}#1\color{black}}
\newcommand{\valerie}[1]{\color{blue}\textbf{From Valerie:}#1\color{black}}

@@

\author{\IEEEauthorblockN{Hoang-Dung Do$^1$, Val\'erie Hayot-Sasson$^1$, Rafael Ferreira da Silva$^3$, Henri Casanova$^2$, Tristan Glatard$^1$
  }\\
  \IEEEauthorblockA{
    $^1$Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada \\
     $^2$Department of Information and Computer Sciences, University of Hawai‘i at Manoa, U.S.A \\
     $^3$Department of Computer Science, University of Southern California, Los Angeles, CA, USA
  }
}

@@

		The data explosion era seen in recent years results in growing needs in 
		data storing, data analysis. 
		Large computing systems including grids, clusters, clouds, peer-to-peer, 
		volunteer computers have been increasingly used to solve the problem. 
		Despite of their powerful computing capability and technological improvements, 
		there are still bottlenecks in these systems. 
		When it comes to I/O, a bottleneck can be seen in the disk I/O due to hardware 
		limitations. Data caching using page cache is one of the solutions applied 
		to minimize disk accesses and improve the I/O performance. 
		In computing system and application optimization studies, one of the 
		effective approaches is using simulation tools to conduct experiments instead 
		of running applications on real infrastructures. 
		Although simulators are built with individual simulation model for each computing 
		resource, the majority does not take page cache into consideration, 
		which can lead to low simulation accuracy in many cases.

		In this paper, we propose a simulation model page cache to simulate I/O 
		with key features of page cache. 
		The model is build with the consideration to allow it to be integrated to 
		existing simulation tools. 
		We also implement the model with SimGrid using WRENCH. 
		Then we create some simulators for different use cases. 
		Finally, we analyze the results, compare them to results of the existing 
		tool as well as real execution.

@@

		In recent years, as a result of the growth of data generated from a variety 
		of data sources, we have seen increasingly growing demands in data storage, 
		processing and analysis. 
		Storing and processing such a massive amount of data require large 
		computing infrastructures. 
		Data processing is a complex process whose the performance is affected 
		by many factors and hindered by bottlenecks in the systems.
		One of the bottlenecks that should be taken into consideration is disk access 
		time due to hardware limitations. 
		Beside hardware technical improvements, architectural solutions have been 
		proposed and implemented in computing systems in order to tackle the 
		disk I/O problem. 
		Caching, a successful technique applied into memory to maximize the 
		I/O performance by keeping data in memory for future accesses,
		has been proving the effectiveness when employed in computer systems.

		Studying in optimizing not only the utilization of page cache but also other 
		computing resources is a need that has never been overlooked.
		The research on computing infrastructures to maximize performance, 
		shorten processing time, and minimize costs gets involved with experiments. 
		However, real platforms are complex and not built for the experimental 
		purposes due to limited and shared resources, operational costs, unstable 
		environments and the result reproducibility difficulties. 
		An alternative approach is to used simulation tools developed for research 
		and experimental purposes.
		The obvious advantages of using simulation are the freedom of choosing 
		simulated infrastructures, reproducible results and low costs.
		These simulators are developed and integrated with simulation models 
		of computing resources including CPU, network and storage.
		However, some reviews over many simulators report that there has been 
		a trade-off between accuracy and scalability due to the level of details in 
		simulation models \cite{casanova2014simgrid} \cite{byrne2017review}.
		Moreover, different simulators are developed by and for a specific community,
		which hinders them from being used in cross-domain.
		SimGrid is a simulation framework developed with the objectives of  
		balancing between accuracy and scalability, as well as versatility.

		In spite of the importance of page cache and the impacts it has on I/O 
		operations, its simulation model is absent in many simulators. 
		Some simulation tools try to model the page cache with cached data, 
		but their models lack of some key features \cite{nunez2012simcan} 
		\cite{nunez2012icancloud}. 
		Moreover, these simulators have a problem in scalability with 
		long simulation time regarding to their very detailed level of simulation.
		Some other works are able to capture some important features of page cache, 
		but they focus on very specific domains \cite{xu2018saving}.

		In this paper, we propose a simulation model of I/O with page cache.
		The model is integrated in WRENCH, an open-source library built 
		on top of SimGrid with more abstract API. 
		Then we evaluate our model with four simulators in four 
		experiment scenarios. 
		This paper is organized as follows. 
		In Section \ref{relatedwork} we provide details of page cache 
		existing simulation tools.
		In Section \ref{relatedwork} we propose our I/O with page 
		cache simulation model and how we implement it and our experiments 
		to evaluate the model.  
		Section \ref{results} compares the results of our model with the results 
		of original WRENCH and real execution results. 
		Finally, Section \ref{discussion} concludes and presents future 
		work.

@@

			In Linux, page cache is a part of memory, which includes pages referring to 
			physical pages on disk \cite{linuxdev3rd2010}. 
			The goal of the page cache is to avoid disk I/O by keeping data in memory 
			for later accesses, minimize I/O time since disk accesses are considerably 
			slower than memory accesses.
			When the kernel starts a read operation, it checks if required data is in page cache.
			If yes, data is read from memory. This is called a \textit{cache hit}. 
			Otherwise, data is read from disk and placed in page cache.
			For writing, page cache is implemented with three different strategies. 
			The first is \textit{direct~I/O} or \textit{no-write}, which means the page cache 
			is not involved in write operations. 
			The second is \textit{write-through}, in which data goes \textit{through} 
			page cache to disk is. In this case, data is written to both page cache and disk. 
			In the third strategy, which is \textit{write-back}, data are written directly 
			to disk as \textit{dirty} pages and these pages will be periodically flushed 
			to disk later by a \textit{writeback} process and then marked as not dirty. 
			The write-back strategy is considered to outperform write-through as well as 
			direct I/O since it delays disk writes and perform in batch later 
			\cite{linuxdev3rd2010}.

			In write-back, one of the keys is the cache eviction mechanism, which 
			removes pages from the page cache when available memory is insufficient. 
			The kernel chooses clean pages from page cache to evict. 
			If the clean pages are inadequate, dirty pages are flushed to disk, 
			marked as clean and available for eviction. 
			Different cache eviction algorithms have been developed and proposed
			\cite{owda2014comparison}.
			In Linux kernel, a \textit{two lists strategy (LRU/2)} is implemented based on 
			the least-recently-used (LRU) scheme, with an \textit{active list} only containing 
			pages accesses more than once, and an \textit{inactive list} containing 
			pages available for eviction. 
			Pages are moved from inactive list to active list if they are 
			accessed when residing in the inactive list. 
			The lists work on LRU manner, pages are added to the tail and removed 
			from the top. 
			The lists are also kept balanced by moving pages from the active list
			to the inactive list when the active list grows too large.

@@

			There has been the research and development of many simulation tools 
			and frameworks for cloud computing with the goal to simulate cloud, grid, 
			HPC platforms, etc. 
			A number of the most famous existing simulators have been analyzed 
			and compared in some reviews (e.g., \cite{byrne2017review}, \cite{casanova2014simgrid}). 
			These simulators provide simulation models of CPU, network, storage 
			with different approaches and levels of details.
			Some simulators are at packet-level, which allows to achieve 
			high simulation accuracy with fine-grain details such as storage simulation 
			in \textit{DiskSim} or network simulation in \textit{CloudSim} 
			and \textit{iCanCloud} \cite{casanova2014simgrid}. 
			However, the issues with the packet-level simulation are scalability due to 
			long simulation time when the simulated platforms and applications grow 
			to hundreds and thousands nodes. 
			SimGrid is an open source simulation platform that has been developed 
			not only to balance the trade-off between accuracy and scalability, 
			but also to achieve versatility, which allows the use of the framework 
			to simulate applications in multiple domains \cite{casanova2014simgrid}.

			However, I/O with page cache model has not been provided in SimGrid. 
			It only simulates storage with capacity and bandwidths.
			Lebre \textit{et al.} adds a storage simulation extension to SimGrid 
			to simulate file system,  but the page cache is not taken into account 
			\cite{lebre2015}. 
			SIMCAN is the simulation framework that models I/O with page cache 
			with data on disk can be kept in page cache \cite{nunez2012simcan}.
			Memory is also modeled in iCanCloud simulator with a component in charge 
			of managing memory accesses and cached data \cite{nunez2012icancloud}, 
			but one of the issues is scalability due to its sophisticated model.
			Ultimately, non of these simulators provide any cache write strategy, 
			cache eviction mechanism with dirty/clean data and the page cache LRU lists. 
			Xu \textit{et al.} applies four cache replacement policies to simulate in-memory 
			caching, but for the study in energy consumption of multi-tier heterogenous 
			network \cite{xu2018saving}.

			In this study, we chose SimGrid to implement our I/O with page cache model
			due to the balancing between accuracy and scalibility, the versatility allowing it 
			to be adopted in different domains, and the design enabling this 
			framework to be extended with new models. 
			The main issue users have to face when using SimGrid is everything has to be 
			implemented from scratch due to its low-level API. 
			To ease this challenge, WRENCH, an open-source library, is built on top 
			of SimGrid to abstract the low-level logic and expose a higher abstraction 
			level API \cite{casanova2018wrench}. 
			We integrate our model in WRENCH and use the SimGrid API to interact with 
			simulated storage resource.
			This approach allows us to leverage existing features in WRENCH and SimGrid.
			The first is the process control, synchronization of resource consumption by 
			concurrent processes handled by the simulation core in SimGrid. 
			The second is the existing SimGrid storage model with capacity and 
			bandwidth properties, which are similar to the characteristics of memory.
			The third is dropping the burden of implementation with the high level 
			of abstraction in WRENCH.

@@

		In this section, we present our approach to model file read and write with
		I/O to page cache, cache eviction and data flushing mechanisms implemented 
		in the Linux kernel. We also detail the design of our simulators and their
		implementation. Finally, we describe experimental scenarios to evaluate
		our simulation model on real applications using a standalone Python
		prototype, SimGrid framework using original WRENCH and the WRENCH version 
		that is integrated with our simulation model (WRENCH-Ext).

@@

            We separate our simulation model in two components, the IO
			Controller and the Memory Manager, which together simulate 
			file read/write mechanisms in Linux (Figure~\ref{fig:interaction}). 
			The Memory Manager simulates I/Os to cache, flushing, periodical flushing, 
			and cache eviction, whereas the IO Controller simulates file reads and writes. 
			Simulated applications can simply interact with the IO Controller instead of 
			calling simulated storage directly as is the case with current simulators.

@@

			We leverage existing storage simulation models to simulate the memory,
			which is characterized with storage capacity, distinguished read/write 
			bandwidths and device latency. 
			All of these features are dealt within models in simulation 
			frameworks, which makes storage models applicable to memory \cite{lebre2015}. 
			In addition, leveraging existing disk models allows us 
			to take advantage of bandwidth sharing between concurrent disk I/O to 
			simulate parallel memory accesses.

			Memory Manager simulates two parallel threads. The first thread is the 
			main thread where activities of applications are simulated, and responsible 
			for the simulation of data flushing, cache eviction and I/Os to cache. 
			The second thread is a simulated background thread, in which Memory Manager 
			periodically searches and flushes expired dirty data in page cache LRU lists 
			to disks.

@@

			Now, page cache LRU lists can be modeled with two lists of data blocks: 
			an active list and an inactive list, ordered by last access time 
			(earliest first, see Figure~\ref{fig:lrulist}).
			As in the kernel, our simulator keeps the size of the active list under
			twice the size of the inactive list by moving least recently 
            used data blocks from the active list to the inactive list.
			Modeling page cache LRU lists as lists of data blocks reduces the
			overhead of the simulator, as data blocks are obviously less
			numerous than file pages, while achieving the accuracy in I/O time
			simulation that can be seen in the later section.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{ulem}

@@

\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:}#1\color{black}}
\newcommand{\english}[1]{\uwave{#1}}

\newcommand{\valerie}[1]{\color{blue}\textbf{From Valerie:}#1\color{black}}

@@

\author{\IEEEauthorblockN{Hoang-Dung Do$^1$, Val\'erie Hayot-Sasson$^1$, Rafael Ferreira da Silva$^3$, Henri Casanova$^2$, Tristan Glatard$^1$
  }\\
  \IEEEauthorblockA{
    $^1$Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
     $^2$Department of Information and Computer Sciences, University of Hawai‘i at Manoa, USA\\
     $^3$Department of Computer Science, University of Southern California, Los Angeles, USA
  }
}

@@

		The data explosion era seen in recent years results in growing needs in 
		data storing, data analysis. 
		Large computing systems including grids, clusters, clouds, peer-to-peer, 
		volunteer computers have been increasingly used to solve the problem. 
		Despite of their powerful computing capability and technological improvements, 
		there are still bottlenecks in these systems. 
		When it comes to I/O, a bottleneck can be seen in the disk I/O due to hardware 
		limitations. Data caching using page cache is one of the solutions applied 
		to minimize disk accesses and improve the I/O performance. 
		In computing system and application optimization studies, one of the 
		effective approaches is using simulation tools to conduct experiments instead 
		of running applications on real infrastructures. 
		Although simulators are built with individual simulation model for each computing 
		resource, the majority does not take page cache into consideration, 
		which can lead to low simulation accuracy in many cases. \tristan{The
		 ideas are fine, but I don't find them well ordered. I think your intro 
		could adopt this logic (1) Computing systems are key to the processing of Big Data, (2) page 
		cache is critical to I/O performance, (3) page cache is not simulated so how 
		can we expect Big Data applications on computing systems to be well simulated? 
		This problem definition should take 2-3 sentences, the bulk of the abstract should be on the paper, not the context.
		}

		In this paper, we propose a simulation model page cache to simulate I/O 
		with key features of page cache. \tristan{The model consists of ...}
		The model is build with the consideration to allow it to be integrated to 
		existing simulation tools. 
		We also implement the model with SimGrid using WRENCH \tristan{people
		 may not know what these things are, characterize them. For instance:
		  "using WRENCH, a SimGrid-based workflow simulator."}. 
		Then we create some simulators for different use cases \tristan{be more specific: characterize the use cases.}. 
		Finally, we analyze the results, compare them to results of the existing 
		tool as well as real execution \tristan{This is too general, 
		you should explain specifically what you found: how is your simulator better than plain simgrid?}.
		\tristan{A conclusion sentence is missing on the impact of your work: how 
		could it be used? what doors does it open? why is it important work?}

@@

		In recent years, as a result of the growth of data generated from a variety 
		of data sources, we have seen increasingly growing demands in data storage, 
		processing and analysis. 
		Storing and processing such a massive amount of data require large 
		computing infrastructures. 
		Data processing is a complex process whose the performance is affected 
		by many factors and hindered by bottlenecks in the systems. \tristan{The previous
		sentences are true but a 
		bit general, everybody knows that, it's a boring way to open a paper. 
		Your first sentences could be more specific to the simulation of big data applications.}
		One of the bottlenecks that should be taken into consideration is disk access 
		time due to hardware limitations. 
		Beside hardware technical improvements, architectural solutions have been 
		proposed and implemented in computing systems in order to tackle the 
		disk I/O problem. 
		Caching, a successful technique applied into memory to maximize the 
		I/O performance by keeping data in memory for future accesses,
		has been proving the effectiveness when employed in computer systems.

		\english{Studying in optimizing not only the utilization of page cache but also other 
		computing resources is a need that has never been overlooked.}
		The research on computing infrastructures to maximize performance, 
		shorten processing time, and minimize costs gets involved with experiments. 
		However, real platforms are complex and not built for the experimental 
		purposes due to limited and shared resources, operational costs, unstable 
		environments and the result reproducibility difficulties. 
		An alternative approach is to used simulation tools developed for research 
		and experimental purposes.
		The obvious advantages of using simulation are the freedom of choosing 
		simulated infrastructures, reproducible results and low costs \tristan{The message of the previous 5 sentences could be summarized in 1 or 2.}.
		These simulators are developed and integrated with simulation models 
		of computing resources including CPU, network and storage.
		However \tristan{why "however" and why is this trade-off important?}, some reviews over many simulators report that there has been 
		a trade-off between accuracy and scalability due to the level of details in 
		simulation models \cite{casanova2014simgrid} \cite{byrne2017review}.
		Moreover, different simulators are developed by and for a specific community \tristan{such as? not sure it's important for our purpose},
		which hinders them from being used in cross-domain.
		SimGrid is a simulation framework developed with the objectives of  
		balancing between accuracy and scalability, as well as versatility.

		In spite of the importance of page cache and the impacts it has on I/O 
		operations, its simulation model is absent in many simulators. 
		Some simulation tools try to model the page cache with cached data, 
		but their models lack of some key features \cite{nunez2012simcan} 
		\cite{nunez2012icancloud} \tristan{which ones?}. 
		Moreover, these simulators have a problem in scalability with 
		long simulation time regarding to their very detailed level of simulation.
		Some other works are able to capture some important features of page cache, 
		but they focus on very specific domains \cite{xu2018saving} \tristan{such as?}.

		In this paper, we propose a simulation model of I/O with page cache \tristan{you should mention what the paper is about earlier in the intro}.
		The model is integrated in WRENCH, an open-source library built 
		on top of SimGrid with more abstract API. 
		Then we evaluate our model with four simulators in four 
		experiment scenarios. 
		This paper is organized as follows. 
		In Section \ref{relatedwork} we provide details of page cache 
		existing simulation tools.
		In Section \ref{relatedwork} we propose our I/O with page 
		cache simulation model and how we implement it and our experiments 
		to evaluate the model.  
		Section \ref{results} compares the results of our model with the results 
		of original WRENCH and real execution results. 
		Finally, Section \ref{discussion} concludes and presents future 
		work.

@@

			In Linux, page cache is a part of memory that includes pages referring to 
			physical pages on disk \cite{linuxdev3rd2010} \tristan{This sounds like a definition but is too vague.}. 
			The goal of the page cache is to avoid disk I/O by keeping data in memory 
			for later accesses, minimize I/O time since disk accesses are considerably 
			slower than memory accesses.
			When the kernel starts a read operation, it checks if required data is in page cache.
			If yes, data is read from memory. This is called a \textit{cache hit}. 
			Otherwise, data is read from disk and placed in page cache.
			For writing, page cache is implemented with three different strategies. 
			The first is \textit{direct~I/O} or \textit{no-write}, which means the page cache 
			is not involved in write operations. 
			The second is \textit{write-through}, in which data goes \textit{through} 
			page cache to disk is \tristan{is what?}. In this case, data is written to both page cache and disk. 
			In the third strategy, called \textit{write-back}, data are written directly 
			to disk as \textit{dirty} pages and these pages will be periodically flushed 
			to disk later by a \textit{writeback} \tristan{spell writeback consistently (dash or no dash?)} process and then marked as not dirty. 
			The write-back strategy is considered to outperform write-through as well as 
			direct I/O since it delays disk writes \english{ and perform in batch later }
			\cite{linuxdev3rd2010}.

			In write-back, one of the keys is the cache eviction mechanism, which 
			removes pages from the page cache when available memory is insufficient. 
			The kernel chooses clean pages from page cache to evict. 
			If the clean pages are inadequate \tristan{why would they be so?}, dirty pages are flushed to disk, 
			marked as clean and available for eviction. 
			Different cache eviction algorithms have been developed and proposed
			\cite{owda2014comparison}.
			In Linux kernel, a \textit{two lists strategy (LRU/2)} is implemented based on 
			the least-recently-used (LRU) scheme, with an \textit{active list} only containing 
			pages accesses more than once, and an \textit{inactive list} containing 
			pages available for eviction \tristan{and accessed how many times?}. 
			Pages are moved from inactive list to active list if they are 
			accessed when residing in the inactive list. 
			The lists work in LRU manner, pages are added to the tail and removed 
			from the top. 
			The lists are also kept balanced by moving pages from the active list
			to the inactive list when the active list grows too large.

@@

			\english{There has been the research and development of many simulation tools 
			and frameworks for cloud computing with the goal to simulate cloud, grid, 
			HPC platforms, etc.} 
			\english{A number of the most famous} existing simulators have been analyzed 
			and compared in some reviews (e.g., \cite{byrne2017review}, \cite{casanova2014simgrid}). 
			These simulators provide simulation models of CPU, network, storage 
			with different approaches and levels of details \tristan{what do the reviews conclude?}.
			Some simulators are at packet-level \tristan{for the network, not a general statement}, which allows to achieve 
			high simulation accuracy with fine-grain details such as storage simulation 
			in \textit{DiskSim} or network simulation in \textit{CloudSim} 
			and \textit{iCanCloud} \cite{casanova2014simgrid}. 
			However, the issues with the packet-level simulation are scalability due to 
			long simulation time when the simulated platforms and applications grow 
			to hundreds and thousands nodes. 
			SimGrid is an open source simulation platform that has been developed 
			not only to balance the trade-off between accuracy and scalability, 
			but also to achieve versatility, which allows the use of the framework 
			to simulate applications in multiple domains \cite{casanova2014simgrid}.

			However, I/O with page cache model has not been provided in SimGrid \tristan{has it been in other simulators?}. 
			It only simulates storage with capacity and bandwidths.
			Lebre \textit{et al.} \tristan{it looks like you're targeting this author, just use the reference as for the other works} adds a storage simulation extension to SimGrid 
			to simulate file system,  but the page cache is not taken into account 
			\cite{lebre2015}. 
			SIMCAN is the \tristan{the or a?} simulation framework that models I/O with page cache 
			\english{with data on disk can be kept in page cache} \cite{nunez2012simcan} \tristan{This paragraph started with Simgrid, so it gives the impression that 
			all these simulators are in simgrid but I don't think they are. Revise.}.
			Memory is also modeled in iCanCloud simulator with a component in charge 
			of managing memory accesses and cached data \cite{nunez2012icancloud}, 
			but one of the issues is scalability due to its sophisticated model.
			Ultimately, non of these simulators provide any cache write strategy, 
			cache eviction mechanism with dirty/clean data and the page cache LRU lists. 
			Xu \textit{et al.} applies four cache replacement policies to simulate in-memory 
			caching, but for the study in energy consumption of multi-tier heterogenous 
			network \cite{xu2018saving}.

			In this study, we chose SimGrid to implement our I/O with page cache model
			due to the balancing between accuracy and scalibility, the versatility allowing it 
			to be adopted in different domains, and the design enabling this 
			framework to be extended with new models. \tristan{you could also mention that it's open source and has been maintained over the past years}
			The main issue users have to face when using SimGrid is everything has to be 
			implemented from scratch due to its low-level API. 
			To ease this challenge, WRENCH, an open-source library, is built on top 
			of SimGrid to abstract the low-level logic and expose a higher abstraction 
			level API \cite{casanova2018wrench}. 
			We integrate our model in WRENCH and use the SimGrid API to interact with 
			simulated storage resource.
			This approach allows us to leverage existing features in WRENCH and SimGrid.
			\english{The first} is the process control, synchronization of resource consumption by 
			concurrent processes handled by the simulation core in SimGrid. 
			\english{The second} is the existing SimGrid storage model with capacity and 
			bandwidth properties, which are similar to the characteristics of memory.
			\english{The third} is dropping the burden of implementation with the high level 
			of abstraction in WRENCH.

@@

		In this section, we present our approach to model file read and write with
		I/O \tristan{"read and write with I/O" seems redundant} to page cache, cache eviction and data flushing mechanisms implemented 
		in the Linux kernel. We also detail the design of our simulators \tristan{are there multiple simulators?} and their
		implementation. Finally, we describe experimental scenarios to evaluate
		our simulation model on real applications using a standalone Python
		prototype, SimGrid framework using original WRENCH and the WRENCH version 
		that is integrated with our simulation model (WRENCH-Ext) \tristan{Introduce the simulator names first, then talk about experiments.}.

@@

            We separate our simulation model in two components, the IO
			Controller and the Memory Manager, which together simulate 
			file read/write mechanisms in Linux (Figure~\ref{fig:interaction}). 
			The Memory Manager simulates I/Os to cache, flushing, periodical flushing \tristan{why is periodical flushing different from flushing?}, 
			and cache eviction, whereas the IO Controller simulates file reads and writes. 
			Simulated applications can simply interact with the IO Controller instead of 
			calling simulated storage directly as is the case with current simulators.

@@

			We leverage existing storage simulation models to simulate the memory,
			which is characterized with storage capacity, \english{distinguished} read/write 
			bandwidths and device latency. 
			\english{All of these features are dealt within models in simulation 
			frameworks, which makes storage models applicable to memory} \cite{lebre2015}. 
			In addition, leveraging existing disk models allows us 
			to take advantage of bandwidth sharing between concurrent disk I/O to 
			simulate parallel memory accesses.

			Memory Manager simulates two parallel threads. The first thread is the 
			main thread where activities of applications are simulated \tristan{unclear, what are "activities of applications"?}, and responsible 
			for the simulation of data flushing, cache eviction and I/Os to cache. 
			The second thread is a simulated background thread, in which Memory Manager 
			periodically searches and flushes expired dirty data in page cache LRU lists 
			to disks \tristan{how about periodical eviction?}.

@@

			\english{Now,} page cache LRU lists can be modeled with two lists of data blocks: 
			an active list and an inactive list, ordered by last access time 
			(earliest first, see Figure~\ref{fig:lrulist}).
			As in the kernel, our simulator keeps the size of the active list under
			twice the size of the inactive list by moving least recently 
            used data blocks from the active list to the inactive list.
			Modeling page cache LRU lists as lists of data blocks reduces the
			overhead of the simulator, as data blocks are obviously less
			numerous than file pages, \english{while achieving the accuracy in I/O time
			simulation that can be seen in the later section}.
